Counterexample-guided Synthesis \\ of Closed-loop Digital Control Systems

### 2016-09-24 paper/paper.tex
add spring-mass damper

%
\begin{equation}
\label{cruise-control-g1}
G_{1}(z)=\frac{1.51z-1.3586}{z-1}.
\end{equation} 
%
\begin{equation}
\label{cruise-control-c1}
C_{1}(z)=\frac{0.0264}{z-0.998}.
\end{equation}

>>>>

The first set of benchmarks considers the discrete plant of a cruise 
control model for the car accounting for rolling friction, aerodynamic drag, 
and gravitational disturbance force~\cite{Astrom08} as follows
%
\begin{equation}
\label{cruise-control-c1}
G_1(z)=\frac{0.0264}{z-0.998}. \nonumber
\end{equation}

Two proportional-integral (PI) controllers are designed by Wang {\it et al.} 
for the cruise control plant $G(z)$~\cite{DBLP:conf/hybrid/WangGRJF16}, 
which has the following mathematical model
%
\begin{equation}
\label{cruise-control-g1}
C_{1}(z)=\frac{1.51z-1.3586}{z-1}, \nonumber
\end{equation} 
%
\begin{equation}
\label{cruise-control-g2}
C_{2}(z)=\frac{2.72z^2 - 4.153z + 1.896}{1.0z^2 - 1.844z + 0.8496}. \nonumber
\end{equation}

The second set of benchmarks considers a simple spring-mass 
damper~\cite{DBLP:conf/hybrid/WangGRJF16}, where both discrete 
plant dynamics and controller are represented by the following 
z-expression, resp.
%
\begin{equation}
\label{spring-mass-damper-g}
G_2(z)=\frac{5\times{10^{-5}}z + 5\times{10^{-5}}}{z^2 - 2z + 1.0001}, \nonumber
\end{equation} 
%
\begin{equation}
\label{spring-mass-damper-c}
C_3(z)=\frac{1.28\times{10^{3}}z^2 - 1.354240\times{10^{3}}z + 0.074879\times{10^{3}}}{z^2 - 1.4990z + 0.4995}. \nonumber
\end{equation}
